IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-10-08 main.tex
:construction: Rephrase results

		\begin{subsection}{Objective and Methodology}
			In this paper, we study an IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g. OFDM) to boost the energy transfer efficiency without creating additional interference. The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff. Different from previous research, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on passive beamforming design. The R-E region characterization problem is transformed into multiple current maximization problems subject to different rate constraints. To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques. Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations. We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively. Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver. Finally, the proposed adaptive IRS design outperformed the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for narrowband SISO transmission.

@@

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided OFDM SWIPT system}
			\label{fi:system}
		\end{figure}

@@

		\begin{subsection}{Energy Harvester}
			\begin{figure}[!t]
				\centering
				\noindent
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
						\resizebox{0.9\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_s$] (0,2);
							\draw (0,2) to [short] (1,2);
							\draw (1,2) to [R=$R_\text{ant}$] (3,2);
							\draw (3,2) to [short] (4,2);
							\draw (4,2) to [R=$R_\text{in}$, v<=$v_{\text{in}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}%
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
						\resizebox{0.9\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_\text{in}$] (0,2);
							\draw (0,2) to [short] (0.25,2);
							\draw (0.25,2) to [D, v<=$v_d$, i=$i_d$] (2.25,2);
							\draw (2.25,2) to [short, -*] (2.5,2);
							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
							\draw (2.5,2) to [short] (4,2);
							\draw (4,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}
				\caption{Rectenna circuits}
			\end{figure}

@@

			When $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD). Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}. Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{ob:irs}. Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The SCA algorithm of phase shift optimization is summarized in Algorithm~\ref{al:irs}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift}
				\label{al:irs}
				\begin{algorithmic}[1]
					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$ for $n=1,\dots,N$, $\boldsymbol{C}_{I/P,n}$ for $n=-N+1,\dots,N-1$
					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$ for $n=-N+1,\dots,N-1$
					\Repeat
						\State $i \gets i + 1$
						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem~\ref{op:irs}
						\State Compute $z^{(i)}$ by \ref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$
						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$, construct $\boldsymbol{\phi}^{\star}$
					\State \textbf{output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}

@@

				\caption{GP: Waveform and Splitting Ratio}

@@

		\begin{subsection}{Alternating Optimization}
			For any direct, incident and reflective channels, we iteratively update the passive beamforming by Algorithm~\ref{al:irs} and waveform, active beamforming, splitting ratio by Algorithm~\ref{al:waveform} until convergence. The AO algorithm is summarized in Algorithm~\ref{al:alternating}.
			\begin{algorithm}[!t]
				\caption{AO: Waveform, Active and Passive Beamforming}
				\label{al:alternating}
				\begin{algorithmic}[1]
					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},P,\sigma_n,\bar{R},Q,\epsilon$
					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
					\Repeat
						\State $i \gets i + 1$
						\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \ref{eq:h_n}, and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
						\State Compute $z^{(i)}$ by \ref{eq:z_irs}
					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State \textbf{output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space WiFi-like environment at a center frequency of \SI{5.18}{\GHz} with reference bandwidth $B=1\,\si{\MHz}$. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path and let $d_H$, $d_V$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$, and choose $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and reference $d_H=2\,\si{\meter}$. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}. Reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. For NLoS channels, all taps are modelled as i.i.d. CSCG random variables. For LoS channels, the first tap, whose power is significantly larger, is in circular uniform distribution while the remaining taps are in i.i.d. CSCG distribution. The average sum-power of all taps is unit such that the multipath response is normalized. All channels are regarded as NLoS unless otherwise mentioned. We choose number of transmit antennas $M=1$, number of reflectors $L=20$, number of subbands $N=16$ as reference, and assume no spatial correlation across active and passive arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$. With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $MP=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands. We also assume \SI{0}{\dBi} IRS element gain and \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over \num{200} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_subband.tex}
			\end{adjustbox}
			\caption{Average R-E region versus the number of subbands}
			\label{fi:re_subband}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/waveform_subband.tex}
			\end{adjustbox}
			\caption{Sorted waveform amplitude versus the number of subbands}
			\label{fi:waveform_subband}
		\end{figure}

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}. Waveform amplitude in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain. Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). However, an excessively large $N$ not only increases computation complexity but also operates out of the small-signal harvester model, thus become prohibitive. \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the tangent WIPT point obtained by PS. Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transceiving strategy, both heavily depends on $N$.

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus the average noise power}
			\label{fi:re_noise}
		\end{figure}

		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}. We \textit{first} note that for a large number of subbands ($N=16$), the R-E region is approximately concave for a high noise level and approximately convex for a low noise level. Hence, TS is preferred at low SNR while PS is preferred at high SNR. This is because at a low SNR, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands. As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested energy via the coupling effect by rectifier nonlinearity. \textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40\,\si{\dBm}$). The reason is that when $\bar{R}$ departs slightly from the capacity, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, since a small amplitude could be inefficient for energy maximization. On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to advantage the of multisine. The result highlights the necessity of joint optimization of waveform and splitting ratio.

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_distance.tex}
			\end{adjustbox}
			\caption{Average R-E region versus AP-IRS horizontal distance}
			\label{fi:re_distance}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/path_loss.tex}
			\end{adjustbox}
			\caption{Path loss versus distance}
			\label{fi:path_loss}
		\end{figure}

		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$. A \textit{first} observation is that, different from the active relay that prefers the middle point, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff. It origins from the product-distance path loss model that applies to finite-size element reflection. As shown in Fig.~\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than \SI{10}{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup, since signal attenuation increases fast at a short distance and experiences marginal effect at a long distance. On the other hand, it also suggests that developing an IRS next to the AP can effectively extend the operation range of SWIPT systems. Considering the passive characteristic of IRS, opportunities are that it can be directly supported by the SWIPT network. A \textit{second} observation is that there exists two optimal IRS development locations that maximizes the path loss production $\Lambda_I\Lambda_R$. It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_reflector.tex}
			\end{adjustbox}
			\caption{Average R-E region versus the number of reflectors}
			\label{fi:re_reflector}
		\end{figure}

>>>>

		\begin{subsection}{Objective and Methodology}
			In this paper, we study an IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multicarrier unmodulated power waveform (deterministic multisine) is superposed to a multicarrier modulated information waveform (e.g. OFDM) to boost the energy transfer efficiency without creating additional interference. The transmit waveform, IRS phase shift and receive splitting ratio are jointly optimized to maximize the R-E tradeoff. Different from previous research, this paper focus on multicarrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on passive beamforming design. The R-E region characterization problem is transformed into multiple current maximization problems subject to different rate constraints. To reduce the design complexity, we propose an Alternating Optimization (AO) algorithm that updates the channel and transceiver iteratively based on Semidefinite Relaxation (SDR) and Geometric Programming (GP) techniques. Numerical results showed that SDR is tight and the proposed algorithm can find a stationary point for all tested channel realizations. We demonstrate that dedicated power waveform can boost the energy transmission efficiency such that TS and PS are preferred at low SNR and high SNR, respectively. Also, IRS brings a significant channel amplification and R-E enhancement especially when deployed next to the transmitter or the receiver. Finally, the proposed adaptive IRS design outperformed the benchmark schemes for broadband transmission, and the optimal IRS can be approximated in closed form for narrowband Single-Input Single-Output (SISO) transmission.

@@

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided OFDM SWIPT system.}
			\label{fi:system}
		\end{figure}

@@

		\begin{subsection}{Energy Harvester}
			\begin{figure}[!t]
				\centering
				\noindent
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[Antenna equivalent circuit\label{ci:antenna_equivalent_circuit}]{
						\resizebox{0.9\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_s$] (0,2);
							\draw (0,2) to [short] (1,2);
							\draw (1,2) to [R=$R_\text{ant}$] (3,2);
							\draw (3,2) to [short] (4,2);
							\draw (4,2) to [R=$R_\text{in}$, v<=$v_{\text{in}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}%
				\begin{minipage}[b]{0.5\linewidth}
					\centering
					\subfloat[A single diode rectifier\label{ci:single_diode_rectifier}]{
						\resizebox{0.9\linewidth}{!}{
							\begin{circuitikz}[transform shape]
							\draw (0,0) to [sV=$v_\text{in}$] (0,2);
							\draw (0,2) to [short] (0.25,2);
							\draw (0.25,2) to [D, v<=$v_d$, i=$i_d$] (2.25,2);
							\draw (2.25,2) to [short, -*] (2.5,2);
							\draw (2.5,2) to [C, l_=$C$, -*] (2.5,0);
							\draw (2.5,2) to [short] (4,2);
							\draw (4,2) to [R=$R_L$, v<=$v_{\text{out}}$, i=$i_{\text{out}}$] (4,0);
							\draw (4,0) to [short] (2,0) node[ground](GND){};
							\draw (2,0) to [short] (0,0);
						\end{circuitikz}
						}
					}
				\end{minipage}
				\caption{Rectenna circuits.}
			\end{figure}

@@

			When $\boldsymbol{\Phi}^{\star}$ is rank-\num{1}, the optimal phase shift vector $\bar{\boldsymbol{\phi}}^\star$ can be obtained by Eigenvalue Decomposition (EVD). Otherwise, a suboptimal solution can be extracted via Gaussian randomization method \cite{Huang2010}. Specifically, we perform EVD $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate $Q$ CSCG random vectors $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1}),\ q=1,\dots,Q$, construct the corresponding candidates $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the one that maximizes the objective function \ref{ob:irs}. Finally, the phase shift is retrieved by $\theta_l=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$. The SCA algorithm of phase shift optimization is summarized in Algorithm~\ref{al:irs}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:irs}
				\begin{algorithmic}[1]
					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho,\sigma_n,\bar{R},Q,\epsilon$
					\State Construct $\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n}$ for $n=1,\dots,N$, $\boldsymbol{C}_{I/P,n}$ for $n=-N+1,\dots,N-1$
					\State \textbf{initialize} $i \gets 0,\boldsymbol{\Phi}^{(0)},t_{I/P,n}^{(0)}$ for $n=-N+1,\dots,N-1$
					\Repeat
						\State $i \gets i + 1$
						\State Obtain $\boldsymbol{\Phi}^{(i)}, t_{I/P,n}^{(i)}$ by solving problem~\ref{op:irs}
						\State Compute $z^{(i)}$ by \ref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Obtain $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Obtain $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $q=1,\dots,Q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, $\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$
						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\phi_l^\star/\phi_{L+1}^\star), \ l=1,\dots,L$, construct $\boldsymbol{\phi}^{\star}$
					\State \textbf{output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}

@@

				\caption{GP: Waveform and Splitting Ratio.}

@@

		\begin{subsection}{Alternating Optimization}
			For any direct, incident and reflective channels, we iteratively update the passive beamforming by Algorithm~\ref{al:irs} and waveform, active beamforming, splitting ratio by Algorithm~\ref{al:waveform} until convergence. The AO algorithm is summarized in Algorithm~\ref{al:alternating}.
			\begin{algorithm}[!t]
				\caption{AO: Waveform, Active and Passive Beamforming.}
				\label{al:alternating}
				\begin{algorithmic}[1]
					\State \textbf{input} $\beta_2,\beta_4,\boldsymbol{h}_{D,n},\boldsymbol{H}_{I,n},\boldsymbol{h}_{R,n},P,\sigma_n,\bar{R},Q,\epsilon$
					\State \textbf{initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{w}_{I/P}^{(0)},\rho^{(0)}$
					\Repeat
						\State $i \gets i + 1$
						\State Fix $\boldsymbol{w}_{I/P}^{(i-1)},\rho^{(i-1)}$ and obtain $\boldsymbol{\phi}^{(i)}$ by Algorithm~\ref{al:irs}
						\State Fix $\boldsymbol{\phi}^{(i)}$, update $\boldsymbol{h}_n^{(i)}$ by \ref{eq:h_n}, and obtain $\boldsymbol{w}_{I/P}^{(i)}, \rho^{(i)}$ by Algorithm~\ref{al:waveform}
						\State Compute $z^{(i)}$ by \ref{eq:z_irs}
					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State \textbf{output} $\boldsymbol{\phi}^{\star}, \boldsymbol{w}_{I/P}^{\star}, \rho^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in the simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space WiFi-like environment at a center frequency of \SI{5.18}{\GHz} with reference bandwidth $B=1\,\si{\MHz}$. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal line parallel to the AP-user path and let $d_H$, $d_V$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_D$, $d_I$, $d_R$ as the length of direct, incident, reflective paths such that $d_I=\sqrt{d_H^2+d_V^2}$, $d_R=\sqrt{(d_D-d_H)^2+d_V^2}$, and choose $d_D=15\,\si{\meter}$, $d_V=2\,\si{\meter}$ and reference $d_H=2\,\si{\meter}$. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}. Reference path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. For NLoS channels, all taps are modelled as i.i.d. CSCG random variables. The average sum-power of all taps is unit such that the multipath response is normalized. All channels are regarded as NLoS unless otherwise mentioned. We choose reference number of transmit antennas $M=1$, reflectors $L=20$, subbands $N=16$, and assume no spatial correlation across active and passive arrays. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\text{ant}}=50\,\si{\ohm}$. With \SI{0}{\dBi} transmit antenna gain, the average Effective Isotropic Radiated Power (EIRP) is fixed to $MP=-36\,\si{\dBm}$ while the reference average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands. We also assume \SI{0}{\dBi} IRS element gain and \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is $Q=10^{3}$, and the R-E region is averaged over \num{200} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to per-subband rate.

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_subband.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:re_subband}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/waveform_subband.tex}
			\end{adjustbox}
			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:waveform_subband}
		\end{figure}

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy. The reason is that although each subband receives a smaller proportion of the total power, more balanced terms are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}. Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \ref{eq:y_I4} and \ref{eq:y_P4}, the only difference of modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain. Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). However, an excessively large $N$ not only increases complexity but also operates out of the small-signal harvester model, thus become prohibitive. \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the tangent WIPT point obtained by PS. Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transceiving strategy, both heavily depends on $N$.

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus $\sigma_n$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_H=2\,\si{\meter}$.}
			\label{fi:re_noise}
		\end{figure}

		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}. We \textit{first} note that for a large number of subbands, the R-E region is approximately concave for a high noise level and approximately convex for a low noise level. Hence, TS is preferred at low SNR while PS is preferred at high SNR. This is because at a low SNR, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands. As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested energy via the coupling effect by rectifier nonlinearity. \textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n \le -40\,\si{\dBm}$). The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm mainly adjusts the splitting ratio $\rho$ rather than put more weight on the multisine waveform, as a small amplitude could be inefficient for energy maximization. On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to advantage the of multisine. The result highlights the necessity of joint optimization of waveform and splitting ratio.

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/re_distance.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $d_H$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $B=1\,\si{\MHz}$.}
			\label{fi:re_distance}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=\linewidth}
				\input{assets/path_loss.tex}
			\end{adjustbox}
			\caption{Path loss versus distance for IEEE TGn channel model D.}
			\label{fi:path_loss}
		\end{figure}

		In Fig.~\ref{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_H$. A \textit{first} observation is that, different from the active relay that favors the midpoint development, placing the IRS closer to either the AP or the user would further improve the R-E tradeoff. It origins from the product-distance path loss model that applies to finite-size element reflection. As shown in Fig.~\ref{fi:path_loss}, although the piecewise TGn path loss model further penalizes large distance (greater than \SI{10}{\meter} for model D), it is still beneficial to have a short-long or long-short transmission setup, since signal attenuation increases fast at a short distance and experiences marginal effect at a long distance. On the other hand, it also suggests that developing an IRS next to the AP can effectively extend the operation range of SWIPT systems. Considering the passive characteristic of IRS, opportunities are that it can be directly supported by the SWIPT network. A \textit{second} observation is that there exist two optimal IRS development locations that maximizes the path loss production $\Lambda_I\Lambda_R$. It implies that more than one IRS may be implemented to further enlarge the R-E region, one attached to the AP and one attached to the IRS.
